---
title: "The Representation Variety of 3-fold symmetry Deligne-Mostow Lattices"
subtitle: "Faculty Research Seminar"  
author: 
  - "Alejandro Ucan-Puc"
  - "j.w. Elisha Falbel and Irene Pasquineli"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(png)
library(grid)
library(knitr)
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(base_color = "#001D8F")
```

```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
```


# _Motivation:_
## How many (different) geometric structures admit a complex manifold?


---
## Some examples of $(G,X)-$structures:
.pull-left[
<span style="font-size:30px">
1. $(Diff(\mathbb{R}^n),\mathbb{R}^n).$
1. $(Hol(\mathbb{C}^n),\mathbb{C}^n).$
1. $(Aff(\mathbb{C}^n,\mathbb{C}^n).$
1. $(PU(1,n),\mathbf{H}^n_{\mathbb{C}}).$
1. $(PGL(n+1,\mathbb{C}),\mathbb{C}\mathbf{P}^n).$
]
---

## How to easy this quest?
--

<span style="font-size:32px"> It is possible to characterize a $(G,X)-$structure by a pair of maps
<br><br>
<span style="font-size:30px"> 1. The __Developping map__ is the map $Dev: \tilde{M} \to X$ where $M$ is the universal cover of the manifold.
--
<br><br>
<span style="font-size:30px"> 2. The __Holonomy representation__ is the map $hol:\pi_1(M)\to G$ where $\pi_1(M)$ is the fundamental group of the manifold.

--
<br><br>
> <span style="font-size:25px"> The pair $(Dev,hol)$ is __unique__.

</span>
---
## What is it known?
<br>
<span style="font-size:30px"> In the case of __complex manifolds__, there is some work related to the first question. 
<br>
--
<br>
<span style="font-size:25px"> 1. Kingler in 1998: characterization of how many different complex projective structures admits a __compact complex manifold.__

<br>
<span style="font-size:25px"> 2. Mok-Yeong in 1993 (Kingler 2001): for __finite volumen _complex hyperbolic manifold_,__ there is a unique complex projective _compatible_ with the hyperbolic one.
</span>
---
## Something to note:
<br>
<span style="font-size:35px"> 1. The Kingler's description is only for __compact__ manifolds.
<br><br>

<span style="font-size:35px"> 2. Mok-Yeong's description only check for __compatibility__ on complex hyperbolic manifolds. 

</span>

---
# _Our case of Interest._
## Deligne-Mostow Lattices 


---
## 3-fold cases and Types
<middle>
.pull-left[
<span style="font-size:30px"> 3-fold Delgine-Mostow lattices belong to the group $PU(2,1)$. Beside: </span>
]
--
.pull-rigth[ 

<span style="font-size:25px"> 1. Have an easy _presentation._ <br>
<span style="font-size:25px"> 2. Have a well-described _fundamental domain._ <br>
<span style="font-size:25px"> 3. Have _low complexity_. <br>
<span style="font-size:25px"> 4. Some associated quotients are _non-compact._ <br>
</span>
]

---
## The general presentation:

<span style="font-size:28px">
$$
\langle J, P, R_1, R_2: J^3=(P^{-1}J)^k=R_1^p=R_2^p=Id, P=R_1 R_2, JR_1 J=R_2 \rangle
$$

</span>


---
## The type 1

<span style="font-size:35px">  The type one Deligne-Mostow lattices are: </span>
   
<span style:"font-size:30px"> __Compact__ :
* $(3,4)$.
* $(3,5)$.
* $(4,3)$.
* $(5,2)$.
* $(5,3)$.
</span>

<span style:"font-size:30px"> __Non-compact__ :
* $(3,6)$.
* $(4,4)$.
* $(6,2)$.
* $(6,3)$.
</span>

---

# _The Algorithm._

<span style="font-size:35px"> __Step 1:__ Normalize the generators. </span>

---

## The (normalized) generating matrices.

---

## The polynomial system
<br>
<span style="font-size:35px"> __Step 2:__ Using the group relations, we create a polynomial systems. 

<br><br><br>
</span>

--



<span style="font-size:35px"> __Step 3:__ We find a Groebner basis, and use it to find the solutions. </span>

---
# _The results_

<span style="font-size:35px"> __Theorem:__ Classification of representation of type one Deligne-Mostow lattices with 3-fold symmetry into $PGL(3,\mathbb{C}):$
<br>

--
<span style="font-size:25px"> 1. Representation preserving generator types are locally rigid.
<br>
<span style="font-size:25px"> 2. Representations without constrains on generators are also locally rigid, except for lattices $(4,3),$ $(4,4)$ and $(6,2)$ which have one dimensional branches for certain representations with regular elliptic generators.

</span>

---
# _Scopes:_
<br> <br>

<span style="font-size:35px"> 1. The 2-fold symmetry $PU(2,1)$ Deligne-Mostow lattices.


</span>


<br> <br>
<span style="font-size:35px"> 2. The Eisenstein-Piccard lattice in $PU(2,1).$
</span>

---

# Thank you!
<br><br>
## `r rmarkdown::metadata$author`  

#### alejandro.ucan-puc@imj-prg.fr
